\documentclass[12pt]{article}
\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{alltt}
\usepackage{array}	
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{verbatim}
\usepackage{setspace}
\usepackage{listings}
\usepackage{amssymb,amsmath, amsthm}

\title{SOEN331: Introduction to Formal Methods\\for Software Engineering\\
Assignment 4 on algebraic specifications}
\author{Tarek Ait Hamouda (40044119), Abhijit Gupta (40066502), \\Ethel Narra Pangan (40061530)}
\date{\today}

\begin{document}
\begin{spacing}{1.5}

\maketitle

\noindent \textbf{Spec}: Location;\\
\noindent \textbf{Sort}: Location;\\
\noindent \textbf{Imports}:String, Point\\
\noindent \textbf{Description}: A location contains a point and a description.
\begin{itemize}
	\item newlocation (String, Point): Creates a new location with the given description and point.
	\item setdescription (String): Modifies the description of a location, and returns the updated location.
	\item getdescription: Returns the description of the location.
	\item setpoint (Point): Modifies the point of the location, and returns the updated location.
	\item getpoint: Returns the point of the location.
\end{itemize}

\noindent \textbf{Operations}:\\
\hspace*{5mm} newlocation: String $\times$ Point $\rightarrow$ Location;\\
\hspace*{5mm} setdescription: String $\times$ Location $\rightarrow$ Location;\\
\hspace*{5mm} getdescription : Location $\rightarrow$ String;\\
\hspace*{5mm} setpoint : Point $\times$ Location $\rightarrow$ Location;\\
\hspace*{5mm} getpoint : Location $\rightarrow$ Point;\\
\noindent \textbf{Variables}:\\
\hspace*{5mm} newDesc, d: String; newPoint, p: Point;\\
\noindent \textbf{Axioms}:\\
\hspace*{5mm} [A1] getdescription(newlocation(d, p)) = d;\\
\hspace*{5mm} [A2] getpoint(newlocation(d, p)) = p;\\
\hspace*{5mm} [A3] setdescription(newDesc, newlocation(d,p)) = newlocation(newDesc, p);\\
\hspace*{5mm} [A4] setpoint(newPoint, newlocation(d,p)) = newlocation(d, newPoint);\\
\newpage
\noindent \textbf{Spec}: Map (Location);\\
\noindent \textbf{Sort}: Map;\\
\noindent \textbf{Imports}: Boolean, Location,$\mathbb{N}$;\\
\noindent \textbf{Description}: A Map ADT contains a collection of locations.
\begin{itemize}
	\item newmap: Creates a new empty map.
	\item addlocation (Location): Adds a new location on the map. A location whose description already exists in the map will override the corresponding location with a new
	point.
Returns updated Map.
	\item deletelocation (String): Deletes the location from the map that corresponds to
	a given description. Returns updated map

	\item containsdescription (String): Determines whether the map contains the given
	description. Returns true if a description is found, and it returns false otherwise.
	\item containspoint (Point): Determines whether the map contains the given point.
	Returns true if a description is found, and it returns false otherwise.
	\item findlocation (String): Returns the point for the location on the map that corresponds to the given description.
	\item isempty: Determines whether the map is empty of annotations. Returns true if the
	map contains no annotations and it returns false otherwise.
	\item clear: Erases all locations from a map.
	\item size: Returns the number of annotations in the map.	
\end{itemize}
\noindent \textbf{Operations}:\\
\hspace*{5mm} newmap: $\rightarrow$ Map;\\
\hspace*{5mm} addlocation: Map $\times$ Location $\rightarrow$ Map;\\
\hspace*{5mm} deletelocation : Map $\times$ String $\rightarrow$ Map;\\
\hspace*{5mm} containsdescription : Map $\times$ String $\rightarrow$ Boolean;\\
\hspace*{5mm} containspoint : Map $\times$ Point  $\rightarrow$ Boolean;\\
\hspace*{5mm} findlocation : Map $\times$ String  $\rightarrow$ Point;\\
\hspace*{5mm} isempty : Map $\rightarrow$ Boolean;\\
\hspace*{5mm} clear : Map $\rightarrow$ Map;\\
\hspace*{5mm} size : Map $\rightarrow$ $\mathbb{N}$ \\
\noindent \textbf{Variables}:\\
\hspace*{5mm} d: String; p, q: Point; loc: Location; map: Map\\
\noindent \textbf{Axioms}:\\
\hspace*{5mm} [A1] isempty(newmap) = true;\\
\hspace*{5mm} [A2] isempty(clear(map)) = true;\\
\hspace*{5mm} [A3] containsdescription(addlocation(map, new), getdescription(loc)) = true;\\
\hspace*{5mm} [A4] containsdescription(map,d) $\rightarrow$ findlocation(addlocation(map, newlocation(d,q)), d) \hspace*{15mm} == q \\
\hspace*{5mm} [A5] size (addLocation(map, newlocation(d,q))) = \\ \hspace*{15mm} \textbf{if} (containsdescription(map, d)) \\ \hspace*{25mm}\textbf{then} size(map) \\ \hspace*{15mm} \textbf{else} size(map) + 1\\
\hspace*{5mm} [A6] isempty(deleteLocation(addlocation(newmap, newlocation(d,p)), d)) = true \\
\hspace*{5mm} [A7] findlocation(addlocation(map, newlocation(d,p)), d) = p\\
\hspace*{5mm} [A8] findlocation(newmap, d) = undefined;\\
\hspace*{5mm} [A9] deletelocation(newmap, d) = undefined;\\
\hspace*{5mm} \textbf{preconditions}:\\
\hspace*{10mm} \textbf{pre} : deletelocation(map: Map, d: String) = containsdescription (map, d);\\
\hspace*{10mm} \textbf{pre} : findlocation(map: Map, d: String) = containsdescription (map, d);\\
\end{spacing}
\end{document}